\section{Dictionary-based Classifier for Other Languages}
\label{sec:dictionary_based_classifier_for_other_languages}
The multilingual side of Wikipedia is one of its main advantages.
%We have argued that one of Wikipedia's main advantages is its 
%the main advantages with Wikipedia is that it is a multilingual encyclopedia. 
Most Wikipedia articles are available in multiple languages. The available languages for an article are shown at the left side of the article. We wanted to take advantage of this property to create dictionary-based classifiers for other languages than just English. 

Our assumption is that we can create dictionary-based classifiers based on the English classifier. This is based on the fact that there are twice as many articles in English than any other language \cite{wiki:wikipedia}. The disadvantage with this approach is that some articles might not be available in English, but might be essential entries in a classifier for the language. 


%This means that it is desirable to take advantage of this and create dictionary-based classifiers for other languages. It is desirable to take advantage of the work already performed for creating the dictionary-based classifier for the English Wikipedia, especially since this this is the most common language.

The file \enwikilanglinks creates a database table which contains information about the available languages for each English Wikipedia article.
%Many Wikipedia articles are available in multiple languages. The file \enwikilanglinks contains information about the language links for the English Wikipedia. 
All language links are represented as entries in \texttt{INSERT} statements on the form
\begin{center}
(\emph{il\_from}, \emph{il\_lang}, \emph{il\_title}).
\end{center}

Table \ref{tab:langlinkdesc} contains the description of the entry fields in each entry 
%\texttt{INSERT} statements  
\cite{wiki:langlinks}, and \ref{fig:langlinkexample} is an example of entries translating English articles to French. The language code \emph{'fr'} determines that the links are between the English Wikipedia articles and the corresponding French Wikipedia articles. 

%This means that it is possible to find all links from English and to another language by finding the language's \emph{language code}. 

\begin{table}[ht]
\renewcommand{\arraystretch}{1.25}
\begin{tabularx}{\textwidth}{l|X}
\textbf{Entry field} &  \textbf{Description} \\ \hline
 il\_from & page\_id of the referring page.\\ \hline
 il\_lang & Language code of the target, in the ISO 639-1 standard. \\  \hline
 il\_title & Title of the target, including namespace 
 (FULLPAGENAMEE style).
\end{tabularx}
\\[10pt]
\caption[Description of the entry fields in the table \emph{Langlink}]{Description of the entries in the table \emph{Langlink}.}
\label{tab:langlinkdesc}
\end{table}

\begin{figure}[h]
\centering
\begin{lstlisting}
INSERT INTO `langlinks` VALUES 
(10642344,'fr','Muro de Aguas'),
(1666460,'fr','Muro de Alcoy'),
(32877065,'fr','Muro en Cameros')
\end{lstlisting}
\caption[Example of langlink \texttt{INSERT} statement]{Example of entries for linking the English ids to the corresponding French articles.}
\label{fig:langlinkexample}
\end{figure}
% INSERT INTO `langlinks` VALUES (865173,'fr','Liste des stations de radio en Autriche'),(6922017,'fr','Liste des stations de radio en Belgique'),(3560441,'fr','Liste des stations de radio en Bielorussie'),
%INSERT INTO `langlinks` VALUES (24190880,'fr','Daniel Zimmermann (personnalité politique)'),(10957102,'fr','Daniel Zueras'),(

\begin{comment}
% Vil jeg ha med dette?
A general approach for creating a dictionary-based classifier for another language is to sort all links between English and the desirable language. Then "translate" the English dictionary by using the page id from the links. 
\end{comment}


\input{Chapters/Implementation/OtherLanguages/Creating_Classifier}
