\subsection{Content Analysis in Advertising}
Automatic content analysis can be found useful in many different settings, but the 
%There are many areas where content analysis (the task of understanding the content of the text) is useful, but the 
two most dominating areas are advertising and improvement of user experience. The focus for this project is to improve advertising, hence, this is our domain.
%Content analysis is useful for understanding texts, and is often used in two domains; advertising and improving user experience. 

Advertising is the main income of most online companies that provide free services. The alternative to advertising is to charge users a fee before they are allowed to use the services. The online market is very competitive and most users expect everything on the Internet to be free. Thus, the most common approach is to provide the services for free, but earn money on advertising instead. 

There are two different roles within online advertising. The advertiser is a person or company that has advertisements available for display, while the publisher is the role that integrates the advertisements on the web page or choose what advertisements the users will see \cite{wiki:onlineadvertising}. Advertisements on frequently visited web pages are usually more expensive than advertisements on less common web pages. Advertisers are also more willing to pay more for advertisements directed towards users with a higher potential of buying the products. 

%free services with advertisement is to sell access to to their services, 

%but this is in many cases not possible because the online market is very competitive and many users expect everything on the Internet to be free. 

%difficult in many cases because of how competitive the market is and the expectations of a free Internet. 
%Online advertising is a growing market and is the main income of many online companies. 
%Online companies have two ways of earning money, they could either let the user pay to use the services or earn money on advertisement. Most web pages choose the second option because the market is very competitive and many web users expects the web pages to be free. %A newspaper might loose readers when trying to charge them. 

%Hence the companies have to earn money without charging the user for their services, and in most cases  this leads to advertisement. 
There are different approaches of paying for advertisements on web pages. The most common ones are Pay-Per-Click (PPC) \cite{wiki:ppc} and Cost-Per-Mille (CPM) \cite{wiki:ppc}. PPC is an approach where the advertiser pays per click on the advertisements, while CPM means that the advertiser pays for showing the advertisement to thousand viewers. 
%Both of these are more profitable if the advertisements are shown to interested users.
%, while PPC means that an advertisement is shown and the advertiser has to pay for each time a user clicks on the advertisement. 
Both of the techniques are more valuable for all parts if the advertisements are shown to people that are interested in the products and more likely to buy the product. The advertiser has a greater chance of getting customers if the advertisement is shown to the right crowd and the publisher can charge a higher price for the advertisement if the advertiser is more pleased with the result of the advertisements.

This means that the advertiser needs to know the users and their interests. Content analysis can be part of building up a profile of the user, since knowing the content of the text viewed to the user can provide information of the interests of the users. 

% TODO: write something about improving user experience