\section{Hidden categories}
Wikipedia's category structure contains lots of hidden categories which are not displayed at the bottom of an article page for the general users, even if the article is placed under the category. Directly under the category \emph{Hidden Categories} are there 15 385 subcategories, where many of these categories' have links to their own hidden subcategories. 


These categories are concerned with maintenance and administration, hence not relevant for our problem. 

which means that if articles 
mostly used for cleanup, where the categories link to articles references need to be ch


not relevant for our task and that we want to sort out of the 

\footnote{en.wikipedia.org/wiki/Category:Hidden\_categories}
Under the structure of Hidden Categories are there 15 385 subcategories, which are not essential.

When looping through \enwikicatlink was 15006 subcategories directly found with links from \emph{Hidden Categories}, which can be marked as not relevant. This reduces number of links relevant between both subcategories and between categories and articles. 

To see the necessity of removing irrelevant categories (the hidden ones), we can look of how number of category and article links are reduced: 
\begin{table}[h]
\centering
\begin{tabular}{l|c|c}
 \textbf{Links between...} & \textbf{W/ Hidden Categories} & \textbf{W/o Hidden Categories}  \\ \hline
 \textbf{subcategories} & 3.341.524 & 2.886.880 \\
 \textbf{articles and categories} & 78.535.744 & 29.034.980 
\end{tabular}
\caption{Number of links removed when links to hidden categories are disregarded}
\label{tab:with_and_without_hidden_cats}
\end{table}

The next step to reduce number of categories and articles are removing those whose titles contains words mostly connected to Wikipedia. All articles with the following words where removed
\emph{articles}, \emph{redirects}, \emph{\_link\_}, \emph{wikipedia}, \emph{wikify}, \emph{wikidata}, \emph{\_pages\_}. 

% 31594 in All_hidden_categories


\ref{tab:removed_irrelevant_words} shows that number of links are reduced when articles and categories containing these words are removed. 

\begin{table}[h]
\centering
\begin{tabular}{l|c|c}
\textbf{Links between...} & \textbf{W/ the words} & \textbf{W/o the words} \\
 \textbf{subcategories}& 2.886.880 & 2.826.161 \\
 \textbf{articles and categories} & 29.034.980 & 24.581.556
\end{tabular}
\caption{Number of links removed when words not likely to be relevant are removed }
\label{tab:removed_irrelevant_words}
\end{table}