\section{Id Mapping}
\label{sec:id_mapping}
The files containing the results becomes extremely large due to the extreme amount of data. All paths to all Wikipedia articles is more than 20 GB of compressed data. It is desirable to reduce the space needed for storing all results on the computer. The solution was to create an id mapping for each category name and article name. Id mapping gives all names a unique id, and instead of writing the full path of category names to the file, we write the full paths with category ids. 

The id mapping is implemented by creating a counter that assigns numbers to each category name or article name that is not found yet, i.e., a unique number represents each name. Figure \ref{fig:idmapping} shows an excerpt of the id mapping created for our purpose, where the id \emph{4600570} corresponds to the article about \emph{Ole-Johan Dahl}, which means that this id is used everywhere \emph{Ole-Johan Dahl} is used in paths. 

\begin{figure}[h]
\centering
\begin{lstlisting}
...
4600566 roger matthews
4600567 pesticide drift
4600568 roxy theatre (clarksville, tennessee)
4600569 papadindar
4600570 ole-johan dahl
4600571 red square (university of washington)
...
\end{lstlisting}
\caption[Id mapping example]{Excerpt of the id mapping between id and the name of all categories and articles.}
\label{fig:idmapping}
\end{figure}

Id mapping is storage efficient because category names and article titles are usually a  lot longer than their representing ids. This means that the disk space needed for storing the id is smaller than the disk space needed for storing the category names or the article titles. 

Working with ids is also faster in many implementations concerning lookups in the program. This depends on the chosen data structure, but dictionaries which are frequently used in our implementation is an example of a data structure that performs faster with id mapping. An example of this is illustrated in figure \ref{fig:id_lookup} where the time to find all categories from the category with id \emph{177678} (corresponding to the category \emph{people}) is 0.955 minutes. Figure \ref{fig:fullname_lookup} shows the time (1.559 minutes) needed to find the same paths for the category names and for the article titles. Comparing the times shows that the time is a lot faster when using ids, which is important when many paths have to found.

\begin{figure}[h]
\centering
\begin{lstlisting}
[INFO] Finding all article paths from 177678

[INFO] Time to find all article paths: 0.955 min
\end{lstlisting}
\caption[Time for all paths for \emph{people} when using ids]{Time needed for finding all paths from the category \emph{177678} (corresponding to the category \emph{people}) when ids are used by our program.}
\label{fig:id_lookup}
\end{figure}


\begin{figure}[h]
\centering
\begin{lstlisting}
[INFO] Finding all article paths from people

[INFO] Time to find all article paths: 1.559 min
\end{lstlisting}
\caption[Time for all paths for \emph{people} when using full names]{Time needed for finding all paths from the category \emph{people} when our program uses full names of categories and articles.}
\label{fig:fullname_lookup}
\end{figure}
 
The last reason to use ids instead of full names is that the full names may include characters useful for describing paths, for instance the characters "/" which is a common way of describing full paths. This could lead to trouble if the category name contains the symbol. 

% Fordel 2: Kan bruke "/" in the text. 

