\chapter*{Acknowledgements}
This study has been a collaboration project between Cxense (\url{http://www.cxense.com}) and the Department of Informatics at the University of Oslo. It was started in the Spring semester 2014 and finished ** 2015. 

First, I would like to express my gratitude to my supervisor Professor Aleksander Øhrn for all his incredibly important feedback and for all the advices he has given me through the process. 
His ideas for this project have been incredible valuable, and his comments have helped me every time I needed help with a problem. I am extremely grateful for his thorough scrutiny of my thesis. 
%all advices he has given me and his scrunity of my thesis. 
I would also like to thank to his colleague Gisle Ytrestøl for all his help, including all the quick responses on email, long discussions about implementations and his never-ending support and optimism about the project. 

A special thanks goes to my study friends, 
% (you guys know who you are)
especially Sindre, Frida and Karine, 
for constantly reminding me how little time I had left, but still supporting me with discussions and good company at the University. I would also like to thank my friend Elisabeth Krampl for motivating me every day and for never asking me to stop talking about my thesis. Your support has been beyond words.

Finally I wish to thank my family for all help, comments, discussions, feedback on what I've written, and most important; for supporting me every day. I could never have done this without any of you. 


\begin{flushright}
Ingrid Grønlie Guren\\
\today
\end{flushright}