\documentclass[a4paper,english]{article}
\usepackage[utf8]{inputenc}         % or whatever you use

\usepackage[T1]{fontenc, url} %andreas
\title{Programs made for the Master Thesis}
\author{Ingrid Grønlie Guren}

\newcommand*\justify{%
  \fontdimen2\font=0.4em% interword space
  \fontdimen3\font=0.2em% interword stretch
  \fontdimen4\font=0.1em% interword shrink
  \fontdimen7\font=0.1em% extra space
  \hyphenchar\font=`\-% allowing hyphenation
}

\newcommand{\enwikipageprops}{\texttt{\justify{enwiki-latest-page\_props.sql.gz}} }
\newcommand{\enwikipage}{\texttt{\justify{enwiki-latest-page.sql.gz}} }
\newcommand{\enwikicatlinks}{\texttt{\justify{enwiki-latest-categorylinks.sql.gz}} }
\newcommand{\allhidden}{\texttt{\justify{All\_hidden\_categories.txt.gz}} }
\newcommand{\enwikiredirect}{\texttt{\justify{enwiki-latest-redirect.sql.gz}} }
\newcommand{\outputredirect}{\texttt{\justify{output-redirect-titles.txt.gz}} }
\newcommand{\subcat}{\texttt{\justify{Sub-categories.txt.gz}} }
\newcommand{\pagecat}{\texttt{\justify{Page-categories.txt.gz}} }
\newcommand{\subcatlink}{\texttt{\justify{Subcat\_links.txt.gz}} }
\newcommand{\catinfo}{\texttt{\justify{category-info.txt}} }
\newcommand{\artinfo}{\texttt{\justify{article-info.txt.gz}} }



\begin{document}

\maketitle{}
\noindent
All programs made for the master thesis, listed in the order they should be run. 

\subsection*{1. Hidden\_Categories.py}
This program is to find all hidden categories in the Wikipedia structure. 
\subsubsection*{Input}
\begin{itemize}
\item[-] \enwikipageprops
\item[-] \enwikipage
\end{itemize}

\subsubsection*{Output}
\begin{itemize}
\item[-] \allhidden : Contains names of all the hidden categories. 
\end{itemize}
Goes through all insert statements in \enwikipageprops and finds all categories marked with \texttt{"hiddencat"}. Then loops through all \enwikipage to find the names of all the hidden categories. 

%\texttt{\justify{enwiki-latest-page.sql.gz}}

\subsection*{2. Redirects.py}
\noindent
Find all titles that should be redirecting and the desirable title

\subsubsection*{Input}
\begin{itemize}
\item[-] \enwikiredirect
\end{itemize}
\subsubsection*{Output}
\begin{itemize}
\item[-] \outputredirect : Contains the page id and titles of all redirects
\end{itemize}
Goes through all insert statements in \enwikiredirect and collect titles and ids of pages redirecting to. 

\subsection*{3. Split\_catlink.py}
Sort all category links between articles and categories to one file, and all category links betweeen categories to another file. 
\subsubsection*{Input}
\begin{itemize}
\item[-] \enwikicatlinks
\item[-] \allhidden 
\item[-] \outputredirect 
\end{itemize}
\subsubsection*{Output}
\begin{itemize}
\item[-] \subcat : All links betweeen categories
\item[-] \pagecat : All links between articles and categories
\end{itemize}
Looks through all links found in \enwikicatlinks and sort depending if the link is between categories or between categories and articles. If the link a category and an article is found, and the article is hidden, the link is disgarded. All category names found in redirect are swapped with the redirecting name. 

\subsection*{4. Remove\_hiddencats.py}
Remove all hidden categories from the links found from \texttt{Split\_catlink.py}
\subsubsection*{Input}
\begin{itemize}
\item[-] \subcat
\item[-] \allhidden
\end{itemize}
\subsubsection*{Output}
\begin{itemize}
\item[-] \subcatlink : All links betweeen categories withouth hidden categories. 
\end{itemize}
Find all children of all hidden categories, and then replace the hidden categories by its children in the links.

\subsection*{5. Categorygraph\_builder.py}
Builds a category graph based on all the links in \subcatlink
\subsubsection*{Input}
\begin{itemize}
\item[-] \subcatlink
\end{itemize}
\subsubsection*{Output}
\begin{itemize}
\item[-] \catinfo : A file containing information about the category graph where all the subcategories of a category is listed under the category name
\end{itemize}

\subsection*{6. Articlegraph\_builder.py}
Create an article graph based on all the links between categories and articles in \pagecat
\subsubsection*{Input}
\begin{itemize}
\item[-] \pagecat : One of the outputs from \texttt{Split\_catlink.py}
\end{itemize}
\subsubsection*{Output}
\begin{itemize}
\item[-] \artinfo : A file containin information about the article graph whelere all the articles of a category is listed under the category name
\end{itemize}

\subsection*{7. Article\_path\_builder-id.py}
Find all possible article paths for all articles in \artinfo
\subsubsection*{Input}
\begin{itemize}
\item[-] \catinfo
\item[-] \artinfo
\end{itemize}


\subsubsection*{Output}
Lots of files containing all possible paths for each article. 

\subsubsection*{}

\subsection*{8. Create\_category\_grades-id.py}

\subsection*{9.  Grader-id.py}

\subsection*{10. Count-parents.py}

\subsection*{11. grade-parser.py}





\end{document}